Microplatforms: Product platforms as code

### 2018-03-14 paper.tex
abstract

\date{\today}% It is always \today, today,
%  but any date may be explicitly specified

\begin{abstract}
	Abstract goes here. Abstract goes here. Abstract goes here. Abstract goes here. Abstract goes here.
	Abstract goes here. Abstract goes here. Abstract goes here. Abstract goes here. Abstract goes here. Abstract goes here.
\end{abstract}

>>>>

\date{\today}

\begin{abstract}
Microplatforms are an automation-based approach of provisioning and operating platforms to run digital products and services, which emphasises autonomy of cross-functional product teams. We discuss the traditional approach of building a large-scale, shared platform and explore the resulting cost to the organisation, chief of which is the cost of coordination between teams. Instead, we offer the concept of each cross-functional team owning and operating a separate, self-contained platform. A key enabler for this approach is full automation - capturing all aspects of the product and the platform from provisioning to service orchestration and policy as source code. This approach results in significantly increased team autonomy and enables agile architecture, continuous deployment to production and ongoing innovation. Microplatforms allow organisations to move engineering effort higher up the value chain and focus on using technology to solve customer problems.
\end{abstract}
